%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Outreach}


\begin{cvhonors}
	
		\cvhonor
	{Member of ``Cazadoras de Estrellas" Project} % Award
	{\textit{DIRVEX, Universidad de Chile. }This outreach project is lead by a group of female graduate students and alumni from the Astronomy Department in Universidad de Chile. The goal is to give high school girls a hands-on experience with astronomical data and meet female astronomers so that they can solve any vocational doubts about this career} 
	{Chile} % Event
	% Location
	{Jul. 2018 - Present} % Date(s)
	
	\cvhonor
	{Public Talk ``Discos protoplanetarios, el origen de los mundos"} % Award
	{Programa Ciencia Abierta, Par Explora RM Norte. Liceo Bicentenario Provincial Santa Teresa de los Andes}
	{Colina, Chile} % Event
	% Location
	{Aug. 30th 2022} % Date(s)
	
	\cvhonor
	{Public Talk ``How to feed baby stars"} % Award
	{\textit{Soapbox Science Munich}} 
	{Munich, Germany} % Event
	% Location
	{Jul. 23rd 2022} % Date(s)

	
	\cvhonor
	{Public Talk ``Eclipses: Luces y Sombras en el Universo"} % Award
	{\textit{Municipalidad de El Bosque.} } 
	{Santiago, Chile} % Event
	% Location
	{Jun. 27th, 2019} % Date(s)

	\cvhonor
	{Public Talk ``Astroinform\'atica para principiantes"} % Award
	{Done at \textit{DUOC UC Puente Alto} and at \textit{Centro de Extensi\'on de la Universidad de Talca}. } 
	{Santiago, Chile} % Event
		% Location
	{Mar. 21st 2019 - Apr. 9th 2019} % Date(s)
	
	\cvhonor
	{Scientific Counselor for ``Festival de Teatro y Ciencias" (FETYC)} % Award
	{\textit{Par Explora Sur Oriente, CONICYT}. The FETYC is a theatre competition organized by the National Comission of Scientific and Technologic Investigation (CONICYT) where several schools prepare a play around a scientific inquiry. The Scientific Counselor guides the scientific content of the plays.} 
	{Santiago, Chile} % Event
	% Location
	{Jun. 2018 - Nov. 2018} % Date(s)
	
	\cvhonor
	{Tourist Guide at National Astronomical Observatory} % Award
	{\textit{Departamento de Astronom\'ia, Universidad de Chile}. } 
	{Santiago, Chile} % Event
	% Location
	{Mar. 2018 - Aug. 2018} % Date(s)
	
\end{cvhonors}