%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Observing experience}
\vspace{8pt}

\begin{cvitems} % Description(s) bullet points
 \item {\textbf{Atacama Large Millimeter/Submillimeter Array (ALMA)}: PI of accepted project 2022.1.00898.S (grade C) ``Quest for the source: connecting a filament to infalling gas towards a protostar in Barnard 5" plus experience with calibration and imaging.}
\item {\textbf{Northern Extended Millimetre Array (NOEMA)}: PI of accepted project W22AH (grade A) ``The connection between streamer and protostellar disk in Per-emb-50" plus experience with calibration and imaging.}
\item {\textbf{Green Bank Telescope (GBT)}: PI and on-site observer of accepted project GBT22B-163 ``Mind the gap: connecting the scales between filaments and protostars" (2022B). Also obtained qualification as remote observer.}
\item {\textbf{IRAM 30m}: PI of accepted project 124-21 ``Go with the flow? Streamer vs. envelope mass infall towards a Class I protostar" (2022A) and remote observing experience for this project. On-site and remote observing experience for project 090-21 (PI: J. Pineda), where I participate as Co-I. Additionally, experience with reduction using CLASS.}
\item {\textbf{Atacama Pathfinder Explorer (APEX)}: PI of accepted project C104-9709 (2019B). On-site observer for Chilean time in three occasions: June 2017 (2017A), April 2018 (2018A) and May 2019 (2019A). Additionally, experience with reduction using CLASS.}
\end{cvitems}