%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Talks}


\cvsubsection{Seminars}

\begin{cvhonors}
	
	 \cvhonor
	{Seminarios de Fis\'ica} % Award
	{\textit{Title: ``Rivers in the sky:  Disrupting Symmetry in Star Formation Through Asymmetric Infall onto Protostars"}, Departamento de F\'isica, Universidad de Santiago de Chile} % Event
	{Santiago, Chile} % Location
	{Nov. 29th 2023} % Date(s)
	
		 \cvhonor
	{Departamento de Astronom\'ia Seminar} % Award
	{\textit{Title: ``Rivers in the sky:  Disrupting Symmetry in Star Formation Through Asymmetric Infall onto Protostars"}, Departamento de Astronom\'ia, Universidad de Chile} % Event
	{Santiago, Chile} % Location
	{Sep. 13th 2023} % Date(s)
	
	 \cvhonor
	{Tuesday UVa / NRAO Astronomy (TUNA) Lunch Talk} % Award
	{\textit{Title: ``Rivers in the sky: streamers discovered towards two young embedded sources in Perseus"}, NRAO} % Event
	{Charlottesville, USA} % Location
	{Dec. 12th 2022} % Date(s)
	
	 \cvhonor
	{IRAM-Wisc-CAS Seminar} % Award
	{\textit{Title: ``Rivers in the sky: streamers discovered towards two young embedded sources in Perseus"}} % Event
	{Virtual} % Location
	{Dec. 12th 2022} % Date(s)
	
	 \cvhonor
	{Star and Planet Formation Seminar} % Award
	{\textit{Title: ``Rivers in the sky: streamers discovered towards two Class I sources in Perseus"}, ESO} % Event
	{Garching, Germany} % Location
	{Nov. 8th 2022} % Date(s)
	
\end{cvhonors}

\cvsubsection{Conferences}

\begin{cvhonors}
	\cvhonor
	{Early Phases of Star Formation} % Award
	{\textit{Title: ``The first systematic search for streamers toward low-mass protostars"}} % Event
	{Ringberg Castle, Kreuth, Germany} % Location
	{May 15th 2024} % Date(s)

	\cvhonor
	{Celebrating 30 Years of Protoplanetary Disk Chemistry: past, present, and future} % Award
	{\textit{Title: ``Streamers: catalysts for physical and chemical changes in protoplanetary disks"}} % Event
	{Ringberg Castle, Kreuth, Germany} % Location
	{Feb. 20th 2024} % Date(s)

	 \cvhonor
	{From Clouds to Planets II: The Astrochemical Link} % Award
	{\textit{Title: ``Rivers in the sky: streamers discovered towards two Class I sources in Perseus"}} % Event
	{Berlin, Germany} % Location
	{Aug. 4th 2022} % Date(s)


	\cvhonor
	{European Astronomical Society Annual Meeting 2022} % Award
	{\textit{Title: ``Rivers in the sky: Streamers discovered towards two embedded protostars in Perseus"}} % Event
	{Valencia, Spain} % Location
	{Jun. 30th 2022} % Date(s)

  \cvhonor
    {Meeting of ALMA Young Astronomers} % Award
    {\textit{Title: ``Rivers in the sky: streamers discovered towards two Class I sources in Perseus"}} % Event
    { Virtual} % Location
    {Mar. 4th 2022} % Date(s)

 
  \cvhonor
    {12th IMPRS Students Symposium} % Event
    {\textit{Title: ``River in the sky: A streamer feeding a Class I protostar"}}% Role
    {Garching, Germany} % Location
    {Nov. 5th 2021} % Date(s)

  \cvhonor
    {Gaps, Rings, Spirals, and Vortices: Structure Formation in Planet-Forming Disks} % Event
    {\textit{Title: ``A Class I protostar with a high streamer mass infall rate"}, Munich Institute for Astro- and Particle Physics} % Role
    {Garching, Germany} % Location
    {Oct. 29th 2021} % Date(s)

  \cvhonor
    {European Astronomical Society Annual Meeting 2021} % Event
    {\textit{Title: ``River in the sky: A streamer feeding a Class I protostar"}} % Role
    {Virtual} % Location
    {Jun. 30th 2021} % Date(s)

  \cvhonor
    {Latin American Regional IAU Meeting 2019} % Event
    {\textit{Title: ``ALMA observations of molecular tracers in R136 in 30Dor: How does cold gas survive?"}, Hotel Antofagasta} % Role
    {Antofagasta, Chile} % Location
    {Nov. 8th 2019} % Date(s)

\end{cvhonors}

